---
title: "PL Report"
author: "Andrew Noecker"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    theme: cerulean
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gt)
library(DT)
library(rvest)
library(tidyverse)

source("R/Period-Reports/pitcher_diff.r")
source("R/Period-Reports/batter_diff.r")
source("R/Period-Reports/rosters.r")
```


```{r Define Termi Roster}
# Termi hitters
termi_hitters <- termis %>%
  inner_join(hitters, by = c("Name" = "HITTERS")) %>%
  pull(Name)

termi_pitchers <- termis %>%
  inner_join(pitchers, by = c("Name" = "PITCHERS")) %>%
  pull(Name)  
```



# **Hitter Reports** {.tabset .tabset-fade .tabset-pills}

## 10 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers

```{r}
batters10 <- fg_batter_stats(Sys.Date() - 10, Sys.Date(), qual = 5) 

termis_hitters10 <- batters10 %>%
  filter(Name %in% termi_hitters)

# termis_hitters15 %>% 
#   gt() %>% 
#   data_color(
#     columns = `Barrel%`,
#     colors = scales::col_numeric(
#       palette = c("red", "orange", "green", "blue"),
#       domain = c(0, 35)
#     )
#   ) %>%
#   data_color(
#     columns = `HardHit%`,
#     colors = scales::col_numeric(
#       palette = c("red", "green"),
#       domain = c(0, 70)
#     )
#   ) %>%
#   tab_header(
#     title = "Termi Hitters 15 Day Report",
#     subtitle = "Arranged in descending barrel%"
#   )

datatable(termis_hitters10, 
          rownames = FALSE,
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```

### MLB

```{r}
datatable(batters10, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```



### Free Agents

```{r}

free_agents10 <- batters10 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents10, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```



## 20 Days {.tabset .tabset-fade .tabset-pills}




### Terminoeckers 

```{r}
batters20 <- fg_batter_stats(Sys.Date() - 20, Sys.Date(), qual = 5) 

termis_hitters20 <- batters20 %>%
  filter(Name %in% termi_hitters)

datatable(termis_hitters20, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### MLB

```{r}
datatable(batters20, filter = 'top',
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### Free Agents

```{r}

free_agents20 <- batters20 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents20, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```



## 30 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers 

```{r}
batters30 <- fg_batter_stats(Sys.Date() - 30, Sys.Date(), qual = 5) 

termis_hitters30 <- batters30 %>%
  filter(Name %in% termi_hitters)

datatable(termis_hitters30, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```


### MLB

```{r}
datatable(batters30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### Free Agents

```{r}

free_agents30 <- batters30 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```


<!-- ## 40 Days {.tabset .tabset-fade .tabset-pills} -->



<!-- ### Terminoeckers  -->

<!-- ```{r} -->
<!-- batters40 <- fg_batter_stats(Sys.Date() - 40, Sys.Date(), qual = 5)  -->

<!-- termis_hitters40 <- batters40 %>% -->
<!--   filter(Name %in% termi_hitters) -->

<!-- datatable(termis_hitters40,  -->
<!--           rownames = FALSE,  -->
<!--           extensions = "FixedColumns", -->
<!--           options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50), -->
<!--   fixedColumns = list(leftColumns = 2), -->
<!--   paging = TRUE,  -->
<!--   scrollX = TRUE,  -->
<!--   searching = TRUE -->
<!-- )) -->

<!-- ``` -->


<!-- ### MLB -->

<!-- ```{r} -->
<!-- datatable(batters40, filter = 'top',  -->
<!--           rownames = FALSE,  -->
<!--           extensions = "FixedColumns", -->
<!--           options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100), -->
<!--   fixedColumns = list(leftColumns = 2), -->
<!--   paging = TRUE,  -->
<!--   scrollX = TRUE,  -->
<!--   searching = TRUE -->
<!-- )) -->
<!-- ``` -->

<!-- ### Free Agents -->

<!-- ```{r} -->

<!-- free_agents40 <- batters40 %>% -->
<!--   anti_join(long_rosters, by = "Name") -->


<!-- datatable(free_agents40, filter = 'top',  -->
<!--           rownames = FALSE,  -->
<!--           extensions = "FixedColumns", -->
<!--           options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100), -->
<!--   fixedColumns = list(leftColumns = 2), -->
<!--   paging = TRUE,  -->
<!--   scrollX = TRUE,  -->
<!--   searching = TRUE -->
<!-- )) -->
<!-- ``` -->



------------

# **Pitcher Reports** {.tabset .tabset-fade .tabset-pills}

## 15 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers

```{r}
pitchers15 <- fg_pitcher_stats(Sys.Date() - 15, Sys.Date(), qual = 2) 

termis_pitchers15 <- pitchers15 %>%
  filter(Name %in% termi_pitchers)

# termis15 %>% 
#   gt() %>% 
#   data_color(
#     columns = `Barrel%`,
#     colors = scales::col_numeric(
#       palette = c("red", "orange", "green", "blue"),
#       domain = c(0, 35)
#     )
#   ) %>%
#   data_color(
#     columns = `HardHit%`,
#     colors = scales::col_numeric(
#       palette = c("red", "green"),
#       domain = c(0, 70)
#     )
#   ) %>%
#   tab_header(
#     title = "Termi Hitters 15 Day Report",
#     subtitle = "Arranged in descending barrel%"
#   )

datatable(termis_pitchers15, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```

### MLB

```{r}
datatable(pitchers15, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### Free Agents

```{r}

free_agents15 <- pitchers15 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents15, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```


## 30 Days {.tabset .tabset-fade .tabset-pills}




### Terminoeckers 

```{r}
pitchers30 <- fg_pitcher_stats(Sys.Date() - 30, Sys.Date(), qual = 2) 

termis_pitchers30 <- pitchers30 %>%
  filter(Name %in% termi_pitchers)

datatable(termis_pitchers30, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### MLB

```{r}
datatable(pitchers30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### Free Agents

```{r}

free_agents30 <- pitchers30 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```



## 45 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers 

```{r}
pitchers45 <- fg_pitcher_stats(Sys.Date() - 45, Sys.Date(), qual = 5) 

termis_pitchers45 <- pitchers45 %>%
  filter(Name %in% termi_pitchers)

datatable(termis_pitchers45, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```


### MLB

```{r}
datatable(pitchers45, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### Free Agents

```{r}

free_agents45 <- pitchers45 %>%
  anti_join(long_rosters, by = "Name")


datatable(free_agents45, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```






<!-- # **Hitter Trends** {.tabset .tabset-fade .tabset-pills} -->

<!-- Examination of who has improved the most over the past 20 days relative to 20 days prior -->

<!-- ## Terminoeckers -->

<!-- Time range 1: **Opening Day** to **`r Sys.Date() - 21`** -->

<!-- Time range 2: **`r Sys.Date()-20`** to **`r Sys.Date()`** -->

<!-- * Note: PA1 is PAs during first time range, PA2 is PAs over last 20 days -->

<!-- ```{r} -->
<!-- hitters_trends <- batter_diff("2023-03-01", # To start of the season -->
<!--             Sys.Date() - 21, -->
<!--             Sys.Date() - 20, -->
<!--             Sys.Date(), -->
<!--             qual1 = 20, -->
<!--             qual2 = 20) %>% -->
<!--     mutate_if(is.numeric, ~round(., 3)) -->


<!-- termis_hitters_trends <- hitters_trends %>% -->
<!--   filter(Name %in% termi_hitters) -->

<!-- datatable(termis_hitters_trends, options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50) -->
<!-- )) -->

<!-- ``` -->


<!-- ## MLB -->

<!-- ```{r} -->
<!-- datatable(hitters_trends, filter = 'top', options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100) -->
<!-- )) -->
<!-- ``` -->

<!-- ------------------------------- -->

<!-- # **Pitcher Trends** {.tabset .tabset-fade .tabset-pills} -->

<!-- Examination of who has improved the most over the past 20 days relative to 20 days prior -->

<!-- ## Terminoeckers -->

<!-- Time range 1: **Opening Day** to **`r Sys.Date() - 21`** -->

<!-- Time range 2: **`r Sys.Date()-20`** to **`r Sys.Date()`** -->

<!-- * Note: IP1 is IPs during first time range, IP2 is IPs over last 20 days -->


<!-- ```{r} -->
<!-- pitchers_trends <- pitcher_diff("2023-03-01", # To start of the season -->
<!--             Sys.Date() - 21, -->
<!--             Sys.Date() - 20, -->
<!--             Sys.Date(), -->
<!--             qual1 = 20, -->
<!--             qual2 = 5) %>% -->
<!--     mutate_if(is.numeric, ~round(., 3)) -->


<!-- termis_pitchers_trends <- pitchers_trends %>% -->
<!--   filter(Name %in% termi_pitchers) -->

<!-- datatable(termis_pitchers_trends, options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50) -->
<!-- )) -->

<!-- ``` -->


<!-- ## MLB -->

<!-- ```{r} -->
<!-- datatable(pitchers_trends, filter = 'top', options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100) -->
<!-- )) -->
<!-- ``` -->





