---
title: "PL Report"
author: "Andrew Noecker"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    theme: cerulean
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gt)
library(DT)
library(rvest)
library(tidyverse)

source("R/Period-Reports/pitcher_diff.r")
source("R/Period-Reports/batter_diff.r")
```


```{r Define Termi Roster}
# Termi hitters
termi_hitters <- c("J.T. Realmuto",
                   "Rowdy Tellez",
                   "Mookie Betts",
                   "Austin Riley",
                   "Corey Seager",
                   "Triston Casas",
                   "Brandon Lowe",
                   "Juan Soto",
                   "Kris Bryant",
                   "Hunter Renfroe",
                   "Lars Nootbaar",
                   "Miguel Vargas",
                   "Cody Bellinger",
                   "Wil Myers",
                   "Garrett Mitchell",
                   "Seth Brown",
                   "Nolan Gorman",
                   "Vaughn Grissom",
                   "Mitch Garver",
                   "Jared Walsh"
                   )

termi_pitchers <- c("Josiah Gray",
                    "Justin Verlander",
                    "Zack Wheeler",
                    "George Kirby",
                    "Lance Lynn",
                    "Seth Lugo",
                    "Felix Bautista",
                    "Seranthony Dominguez",
                    "Nathan Eovaldi",
                    "David Peterson",
                    "Clarke Schmidt",
                    "Mitch Keller",
                    "Nick Martinez",
                    "Alex Lange",
                    "Brandon Pfaadt",
                    "Triston McKenzie"
                    )
```



# **Hitter Reports** {.tabset .tabset-fade .tabset-pills}

## 10 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers

```{r}
batters10 <- fg_batter_stats(Sys.Date() - 10, Sys.Date(), qual = 5) 

termis_hitters10 <- batters10 %>%
  filter(Name %in% termi_hitters)

# termis_hitters15 %>% 
#   gt() %>% 
#   data_color(
#     columns = `Barrel%`,
#     colors = scales::col_numeric(
#       palette = c("red", "orange", "green", "blue"),
#       domain = c(0, 35)
#     )
#   ) %>%
#   data_color(
#     columns = `HardHit%`,
#     colors = scales::col_numeric(
#       palette = c("red", "green"),
#       domain = c(0, 70)
#     )
#   ) %>%
#   tab_header(
#     title = "Termi Hitters 15 Day Report",
#     subtitle = "Arranged in descending barrel%"
#   )

datatable(termis_hitters10, 
          rownames = FALSE,
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```

### MLB

```{r}
datatable(batters10, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

## 20 Days {.tabset .tabset-fade .tabset-pills}




### Terminoeckers 

```{r}
batters20 <- fg_batter_stats(Sys.Date() - 20, Sys.Date(), qual = 5) 

termis_hitters20 <- batters20 %>%
  filter(Name %in% termi_hitters)

datatable(termis_hitters20, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### MLB

```{r}
datatable(batters20, filter = 'top',
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```


## 30 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers 

```{r}
batters30 <- fg_batter_stats(Sys.Date() - 30, Sys.Date(), qual = 5) 

termis_hitters30 <- batters30 %>%
  filter(Name %in% termi_hitters)

datatable(termis_hitters30, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```


### MLB

```{r}
datatable(batters30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

## 40 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers 

```{r}
batters40 <- fg_batter_stats(Sys.Date() - 40, Sys.Date(), qual = 5) 

termis_hitters40 <- batters40 %>%
  filter(Name %in% termi_hitters)

datatable(termis_hitters40, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```


### MLB

```{r}
datatable(batters40, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```


------------

# **Pitcher Reports** {.tabset .tabset-fade .tabset-pills}

## 15 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers

```{r}
pitchers15 <- fg_pitcher_stats(Sys.Date() - 15, Sys.Date(), qual = 2) 

termis_pitchers15 <- pitchers15 %>%
  filter(Name %in% termi_pitchers)

# termis15 %>% 
#   gt() %>% 
#   data_color(
#     columns = `Barrel%`,
#     colors = scales::col_numeric(
#       palette = c("red", "orange", "green", "blue"),
#       domain = c(0, 35)
#     )
#   ) %>%
#   data_color(
#     columns = `HardHit%`,
#     colors = scales::col_numeric(
#       palette = c("red", "green"),
#       domain = c(0, 70)
#     )
#   ) %>%
#   tab_header(
#     title = "Termi Hitters 15 Day Report",
#     subtitle = "Arranged in descending barrel%"
#   )

datatable(termis_pitchers15, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```

### MLB

```{r}
datatable(pitchers15, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

## 30 Days {.tabset .tabset-fade .tabset-pills}




### Terminoeckers 

```{r}
pitchers30 <- fg_pitcher_stats(Sys.Date() - 30, Sys.Date(), qual = 2) 

termis_pitchers30 <- pitchers30 %>%
  filter(Name %in% termi_pitchers)

datatable(termis_pitchers30, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```

### MLB

```{r}
datatable(pitchers30, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```


## 45 Days {.tabset .tabset-fade .tabset-pills}



### Terminoeckers 

```{r}
pitchers45 <- fg_pitcher_stats(Sys.Date() - 45, Sys.Date(), qual = 5) 

termis_pitchers45 <- pitchers45 %>%
  filter(Name %in% termi_pitchers)

datatable(termis_pitchers45, 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))

```


### MLB

```{r}
datatable(pitchers45, filter = 'top', 
          rownames = FALSE, 
          extensions = "FixedColumns",
          options = list(
  pageLength = 20,
  legnthMenu = c(5, 10, 20, 50, 100),
  fixedColumns = list(leftColumns = 2),
  paging = TRUE, 
  scrollX = TRUE, 
  searching = TRUE
))
```





<!-- # **Hitter Trends** {.tabset .tabset-fade .tabset-pills} -->

<!-- Examination of who has improved the most over the past 20 days relative to 20 days prior -->

<!-- ## Terminoeckers -->

<!-- Time range 1: **Opening Day** to **`r Sys.Date() - 21`** -->

<!-- Time range 2: **`r Sys.Date()-20`** to **`r Sys.Date()`** -->

<!-- * Note: PA1 is PAs during first time range, PA2 is PAs over last 20 days -->

<!-- ```{r} -->
<!-- hitters_trends <- batter_diff("2023-03-01", # To start of the season -->
<!--             Sys.Date() - 21, -->
<!--             Sys.Date() - 20, -->
<!--             Sys.Date(), -->
<!--             qual1 = 20, -->
<!--             qual2 = 20) %>% -->
<!--     mutate_if(is.numeric, ~round(., 3)) -->


<!-- termis_hitters_trends <- hitters_trends %>% -->
<!--   filter(Name %in% termi_hitters) -->

<!-- datatable(termis_hitters_trends, options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50) -->
<!-- )) -->

<!-- ``` -->


<!-- ## MLB -->

<!-- ```{r} -->
<!-- datatable(hitters_trends, filter = 'top', options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100) -->
<!-- )) -->
<!-- ``` -->

<!-- ------------------------------- -->

<!-- # **Pitcher Trends** {.tabset .tabset-fade .tabset-pills} -->

<!-- Examination of who has improved the most over the past 20 days relative to 20 days prior -->

<!-- ## Terminoeckers -->

<!-- Time range 1: **Opening Day** to **`r Sys.Date() - 21`** -->

<!-- Time range 2: **`r Sys.Date()-20`** to **`r Sys.Date()`** -->

<!-- * Note: IP1 is IPs during first time range, IP2 is IPs over last 20 days -->


<!-- ```{r} -->
<!-- pitchers_trends <- pitcher_diff("2023-03-01", # To start of the season -->
<!--             Sys.Date() - 21, -->
<!--             Sys.Date() - 20, -->
<!--             Sys.Date(), -->
<!--             qual1 = 20, -->
<!--             qual2 = 5) %>% -->
<!--     mutate_if(is.numeric, ~round(., 3)) -->


<!-- termis_pitchers_trends <- pitchers_trends %>% -->
<!--   filter(Name %in% termi_pitchers) -->

<!-- datatable(termis_pitchers_trends, options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50) -->
<!-- )) -->

<!-- ``` -->


<!-- ## MLB -->

<!-- ```{r} -->
<!-- datatable(pitchers_trends, filter = 'top', options = list( -->
<!--   pageLength = 20, -->
<!--   legnthMenu = c(5, 10, 20, 50, 100) -->
<!-- )) -->
<!-- ``` -->





